# Practical Machine Learning Prediction Assignment
### Yujing Cao      1/10/2015

# Goal
In this prediction assignment, we use the provided dataset to predict the manner in which people did the exercise. The following packages are used 
```{r}
library(Hmisc)
library(caret)
library(randomForest)
library(rattle)
library(rpart.plot)
set.seed(2015)
options(warn=-1)
```
# Download Datasets
```{r}
dataset_Train=read.csv("pml-training.csv",head=T)
dataset_Test=read.csv("pml-testing.csv",head=T)
```
# Cleaning Data
First, replace all the blanks ("") and "#DIV/0" with "NA", then remove all the columns which contain NAs
```{r}
Train_clean=read.csv("pml-training.csv",na.strings=c("","#DIV/0","NA"))
Test_clean=read.csv("pml-testing.csv",na.strings=c("","#DIV/0","NA"))
Train_clean=Train_clean[,colSums(is.na(Train_clean))==0]
Test_clean=Test_clean[,colSums(is.na(Test_clean))==0]
```
The features user_name,raw_timestamp_part_1,raw_timestamp_part_2,cvtd_timestamp,new_window,num_windoware not related to calculations and are removed form the downloaded data. 
```{r}
Train_clean=Train_clean[,-c(1:7)]
Test_clean=Test_clean[,-c(1:7)]
```
# Split Train_clean into training set and testng set
```{r}
inTrain=createDataPartition(Train_clean$classe,p=0.75,list=FALSE)
training=Train_clean[inTrain,]
testing=Train_clean[-inTrain,]
```
# Building a model based on Decision Tree
```{r}
modelFit1=train(classe~.,data=training,method="rpart")
print(modelFit1$finalModel)
fancyRpartPlot(modelFit1$finalModel,main="Classification Tree")
```
# Building a model based on Random Forest
```{r}
modelFit2=randomForest(classe~.,data=training)
```
# Compare modelFit1 and modelFit2 based the accuracy
```{r}
Accuracy1=confusionMatrix(testing$classe,predict(modelFit1,testing))
Accuracy2=confusionMatrix(testing$classe,predict(modelFit2,testing))
Accuracy1$overall[1]
Accuracy2$overall[1]
```
Since accuracy of modelFit2 is much higher than modelFit1, we would choose modelFit2 to do prediction.
# Test Data Submit
The following submisson code are from project assignment instruction.
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
Prediction=predict(modelFit2,Test_clean)
Prediction
pml_write_files(Prediction)
```